Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome

### 2016-05-25 submission/Sze_Obesity_PeerJ_2016_Supp.Rmd
Table S1 creation and removing old data links

OverallPValue <- read.csv("results/tables/denovoOverallPTable.csv")
ShannonRRTable <- read.csv("results/tables/denovoShannonRRTable.csv")
BFRatioRRTable <- read.csv("results/tables/denovoBFRatioRRTable.csv")

@@

Study <- as.character(OverallPValue$X)
Bacteroidetes <- format(round(OverallPValue$Bacteroidetes, 2), nsmall=2)
Firmicutes <- format(round(OverallPValue$Firmicutes, 2), nsmall=2)
BFRatio <- format(round(OverallPValue$BFRatio, 2), nsmall=2)
Shannon <- format(round(OverallPValue$Shannon, 2), nsmall=2)
OTURich <- format(round(OverallPValue$OTURich, 2), nsmall=2)
Evenness <- format(round(OverallPValue$Evenness, 2), nsmall=2)
BrayC <- format(round(OverallPValue$BrayC, 2), nsmall=2)

@@

![Figure S1](results/figures/suppFigClostridiales.png)\

@@

![Figure S2](results/figures/suppFigLachno.png)\

@@

![Figure S3](results/figures/suppFigRumi.png)\

@@

```{r Table_S2, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r Table_S3, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r Figure_S4, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/", dev = c("pdf", "png")}

@@

```{r Figure_S5, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/", dev = c("pdf", "png")}

@@

```{r Figure_S6, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/", dev = c("pdf", "png")}

@@

```{r Figure_S7, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/", dev = c("pdf", "png")}

@@

```{r Figure_S8, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/", dev = c("pdf", "png")}

@@

```{r Figure_S9, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/", dev = c("pdf", "png")}

@@

```{r Figure_S10, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/", dev = c("pdf", "png")}

>>>>

alpha_tests.summary <- read.table("../data/process/alpha_tests.summary", header=T)
beta_tests.summary <- read.table("../data/process/beta_tests.summary", header=T)
```

@@

Study <- unique(as.character(alpha_tests.summary$dataset))
Bacteroidetes <- format(round(alpha_tests.summary[
  which(alpha_tests.summary$metric == 'bacteroidetes'), 'p.value'], 3), nsmall=3)
Firmicutes <- format(round(alpha_tests.summary[
  which(alpha_tests.summary$metric == 'firmicutes'), 'p.value'], 3), nsmall=3)
BFRatio <- format(round(alpha_tests.summary[
  which(alpha_tests.summary$metric == 'bf_ratio'), 'p.value'], 3), nsmall=3)
Shannon <- format(round(alpha_tests.summary[
  which(alpha_tests.summary$metric == 'shannon'), 'p.value'], 3), nsmall=3)
OTURich <- format(round(alpha_tests.summary[
  which(alpha_tests.summary$metric == 'sobs'), 'p.value'], 3), nsmall=3)
Evenness <- format(round(alpha_tests.summary[
  which(alpha_tests.summary$metric == 'shannoneven'), 'p.value'], 3), nsmall=3)
BrayC <- format(round(beta_tests.summary$p_value, 3), nsmall=3)

@@

@@

@@

@@

```{r Table_S2, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}

@@

```{r Table_S3, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}

@@

```{r Figure_S4, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE,  fig.path="results/figures/", dev = c("pdf", "png")}

@@

```{r Figure_S5, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE,  fig.path="results/figures/", dev = c("pdf", "png")}

@@

```{r Figure_S6, echo=FALSE, message=FALSE, warning=FALSE, eval = FALSE,  fig.path="results/figures/", dev = c("pdf", "png")}

@@

```{r Figure_S7, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE,  fig.path="results/figures/", dev = c("pdf", "png")}

@@

```{r Figure_S8, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE,  fig.path="results/figures/", dev = c("pdf", "png")}

@@

```{r Figure_S9, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE,  fig.path="results/figures/", dev = c("pdf", "png")}

@@

```{r Figure_S10, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE,  fig.path="results/figures/", dev = c("pdf", "png")}
